\chapter{Negative Present Tense}
\section*{Vocabulary}
\begin{itemize}
	\item \textbf{alegra} [\textit{ni}]: duck
	\item \textbf{eshina} [\textit{ni}]: fish
	\item \textbf{hrakkar} [\textit{ni}]: white lion
	\item \textbf{ovethat} [\textit{v-at}]: to fly
	\item \textbf{zerqolat} [\textit{v-lat}]: to swim
	\item \textbf{vrelat} [\textit{v-at}]: to leap
\end{itemize}
\section*{Text}
\textbf{Alegra ovetha. Anha vos ovethok. Yeri vos ovethi. Me vos ovetho. Kisha vos ovethoki.}
\textbf{Eshina zerqoe. Anha vos zerqok. Yeri vos zerqoo. Me vos zerqoo. Kisha vos zerqoki.}
\textbf{Hrakkar vrela. Anha vos vrelok. Yeri vos vreli. Me vos vrelo. Kisha vos vreloki.}
\section*{Grammar}
\subsection*{Negative Present Tense}
When conjugating verbs in the negative present tense, \textbf{vos} is always required before the conjugated verb. It can
be said that \textbf{vos} is a direct translation of the English word ``not'', which has the same linguistic function, to negate a verb in
a sentence.
\subsection*{Conjugation Table}
Below is a conjugation table for the negative present tense. \\
\begin{tabular}{|c|c|c|c|c|}
		\hline
		Pronoun & \textbf{-at} & \textbf{ifat} & \textbf{-lat} & \textbf{dothralat} \\
		\hline
		\textbf{anha} & \textbf{vos -ok} & \textbf{vos ifok} & \textbf{vos -ok} & \textbf{vos dothrok} \\
		\hline
		\textbf{yer} & \textbf{vos -i} & \textbf{vos ifi} & \textbf{vos -o} & \textbf{vos dothrao} \\
		\hline
		\textbf{me} & \textbf{vos -o} & \textbf{vos ifo} & \textbf{vos -o} & \textbf{vos dothrao} \\
		\hline
		\textbf{kisha} & \textbf{vos -oki} & \textbf{vos ifoki} & \textbf{vos -oki} & \textbf{vos dothroki} \\
		\hline
		\textbf{yeri} & \textbf{vos -i} & \textbf{vos ifi} & \textbf{vos -o} & \textbf{dothrao} \\
		\hline
		\textbf{mori} & \textbf{vos -i} & \textbf{vos ifi} & \textbf{vos -o} & \textbf{dothrao} \\
		\hline
\end{tabular}
\section*{Exercises}
\begin{enumerate}
	\item Conjugate the following verbs in the negative present tense. You can assume here that all verbs that end in
				\textbf{-lat} are \textbf{-lat} verbs.
	\begin{enumerate}
		\item \textbf{aranat}
		\item \textbf{arthasolat}
		\item \textbf{atholat}
		\item \textbf{emat}
	\end{enumerate}
	\item Translate the following English sentences into Dothraki.
	\begin{enumerate}
		\item The duck lives.
		\item The white lion does not fly.
		\item The fish do not learn.
		\item They do not swim.
	\end{enumerate}
\end{enumerate}
